### 2020-08-13 5_evaluation.tex

PaRSEC, StarPU and Regent
rely on runtime analysis that can suffer from
scalability bottlenecks if every node must consider the tasks
executing on all other nodes. PaRSEC DTD and StarPU mitigate this
partially by allowing the user to omit tasks not directly
dependent on those executed by a given node. However, this approach still requires checks that scale with
node count and thus limit scalability~\cite{PARSEC_DTD}. Compile-time analysis can
partially or fully mitigate this overhead. PaRSEC PTG improves over DTD 
by performing DAG expansion at compile time~\cite{PARSEC_DTD}, but
retains dynamic checks that limit scalability. PaRSEC shard includes additional manual optimizations over DTD, completely eliminating these dynamic checks. Regent
uses a compile-time optimization to improve
scalability~\cite{ControlReplication17}; the increase in METG beyond 16 nodes is due to a known bug in Realm barrier migration which the Realm Task Bench implementation is able to manually work around.

>>>>

PaRSEC, StarPU and Regent
rely on runtime analysis that can suffer from
scalability bottlenecks if every node must consider the tasks
executing on all other nodes. PaRSEC DTD and StarPU mitigate this
partially by allowing the user to omit tasks not directly
dependent on those executed by a given node. However, this approach still requires checks that scale with
node count and thus limit scalability~\cite{PARSEC_DTD}. Compile-time analysis can
partially or fully mitigate this overhead. PaRSEC PTG improves over DTD 
by performing DAG expansion at compile time~\cite{PARSEC_DTD}, but
retains dynamic checks that limit scalability. PaRSEC
\lstinline{shard} includes additional manual optimizations over DTD,
completely eliminating these dynamic checks. StarPU \lstinline{expl}
is written in an explicitly parallel style using MPI for
communication, and thus avoids this bottleneck. Regent uses a
compile-time optimization that improves scalability with no user
intervention~\cite{ControlReplication17}. We see that all of PaRSEC
\lstinline{shard}, StarPU \lstinline{expl}, and Regent are able to
achieve optimal scalability.
